paper1_figures

### 2023-09-11 paper1_markdown.Rmd
Update paper1_markdown.Rmd
test
Sabina 11.09

classoption       : "man"
output            : papaja::apa6_word

---

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
Classical economic theories have described human being as "homo economicus". This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954]. Therefore, according to these theories, human beings are not supposed to show altruistic behaviours, i.e. behaviours that involve costs for the self while benefiting others [@Wittek2015]. However, prosocial acts are often observed in human interactions (**FIND REFERENCES**), and many theories have been developed to explain them.
An example is the theory of competitive altruism [@Roberts1998], that says that acting for the good of others could be a signal of a person's prosociality and therefore improve this person's reputation. Moreover, in the evolutionary perspective, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995].
Adding something on cooperation norms? Maybe this could be the link between altruism and cooperation? See also the article in Zotero that says that altruism is one of the seven forms that cooperation could have, so maybe is it better to talk about cooperation from the beginning???

@@

where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980]. **<- EXPLAIN BETTER!!!**

@@

b.	Moreover, some studies consider cooperation to be the intuitive option, while defection needs more thinking (Kieslich & Hilbig, 2014)
c.	A deeper understanding of mechanisms underlying cooperation in social dilemma is therefore necessary
+ cooperation even more fragile when scarce resources (De Luca et al.) => importance of understanding it

@@

-	This is even more important if we consider the practical implication that social dilemmas have in our society: social dilemmas could be translated into commons
a.	Climate change as social dilemmas
b.	Definition of commons  commons as social dilemmas
c.	Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
d.	But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
e.	Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)
-	Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
-	Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members
a.	?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016
-	Research questions (see if not too redundant with the previous phrase)

+ introducing free-riding concept somewhere

# Methods
To conduct this scoping review, different papers published in academic journals were analyzed in response to the research questions. 
To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect. The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust" **, "intergroup"**, and they were paired with "AND" and "OR" Boolean operators. The research was made during the month of August, 2023.
According with @Munn2022, the type of source was not a selection criteria, therefore experimental and qualitative studies, as well as meta-analysis and systematic reviews are included. This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas. Moreover, there were not chronological or geographical limitations, once again to provide a broader vision on the topic.
There were however some selection criteria concerning the papers' content. First of all, as mentioned in the introduction, this review will focus on individual and group dynamic that can enhance or decrease cooperation in a social dilemma situation (i. e. commons). For this reason, all the papers investigating how an external entity/institution can shape cooperation were not included. Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded. **include explication**

@@

# Individual factors
## Gender
The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no difference between genders. In general, meta-analysis found a non significant effect size for this difference [e.g. @Balliet2011; @Spadaro2023]. This indicates that gender differences in cooperation are very flexible and can vary depending on the context [@Spadaro2023]. Therefore, when a significant effect is observed, it means that gender has somewhat been made salient by the situation [@Sell2009].

@@

## Group identity
@Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation

# Discussion

>>>>

classoption       : "man"
output            : papaja::apa6_word
---

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Classical economic theories have described human being as "homo economicus". This means that, facing a choice, individuals are considered as completely rational and always maximizing (expected) utility [@Edwards1954]. Therefore, according to these theories, human beings are not supposed to show altruistic behaviours, i.e. behaviours that involve costs for the self while benefiting others [@Wittek2015]. However, prosocial acts are often observed in human interactions (**FIND REFERENCES**), and many theories have been developed to explain them. An example is the theory of competitive altruism [@Roberts1998], that says that acting for the good of others could be a signal of a person's prosociality and therefore improve this person's reputation. Moreover, in the evolutionary perspective, the capacity to endorse a personal cost communicates strength and wealth, socially valued characteristics [@Zahavi1995]. Adding something on cooperation norms? Maybe this could be the link between altruism and cooperation? See also the article in Zotero that says that altruism is one of the seven forms that cooperation could have, so maybe is it better to talk about cooperation from the beginning???

@@

where each individual's payoff is higher with an egoistic, non-cooperative behaviour (no matter what others do), but where the best individual outcome is reached when everybody cooperates [@Dawes1980]. **\<- EXPLAIN BETTER!!!**

@@

b.  Moreover, some studies consider cooperation to be the intuitive option, while defection needs more thinking (Kieslich & Hilbig, 2014)
c.  A deeper understanding of mechanisms underlying cooperation in social dilemma is therefore necessary

-   cooperation even more fragile when scarce resources (De Luca et al.) =\> importance of understanding it

@@

-   This is even more important if we consider the practical implication that social dilemmas have in our society: social dilemmas could be translated into commons

a.  Climate change as social dilemmas
b.  Definition of commons  commons as social dilemmas
c.  Article that says that social dilemmas are not the same as commons (Cole & Grossman, 2010)
d.  But: Reindl et al. (2019) and Rommel et al. (2015)  behaviour in social dilemmas is informative about behaviours in commons + @Balliet2011: in the introduction (pages 1-2) there is a good explanation of social dilemma's utility to investigate cooperation
e.  Existing theory about the commons = similar structure than for social dilemmas: rational human beings are supposed to fail (TOC, Hardin, 1986), but in reality cooperation is often observed (for example Ostrom, 1990 + find others)

-   Importance of commons: Pacheco et al. (2014) having small groups behaving in an ecological way is efficient against climate change  very important to understand under which conditions cooperation could be enhanced in commons
-   Aim of this scoping review = shed light on cooperation both in social dilemmas and in commons by (1) identifying individual factors that can enhance it and (2) understanding what kind of group organization groups can set to improve a cooperation of all members

a.  ?? Is it to mention that I focus on what a group can do, without focusing on how external institutions can influence cooperation?? If so, see @Larsson2016

-   Research questions (see if not too redundant with the previous phrase)

-   introducing free-riding and defection concept somewhere (see @Gomez-Ruiz2020 introduction for free-riding)

# Methods

To conduct this scoping review, different papers published in academic journals were analyzed in response to the research questions. To gather the papers, a Boolean search methodology was used in different scientific search engines such as Scopus, Web of Science and ScienceDirect. The key phrases were "social dilemma", "public good", "common resource", "commons", "cooperation", "conflicts", "reciprocity", "trust" **, "intergroup"**, and they were paired with "AND" and "OR" Boolean operators. The research was made during the month of August, 2023. According with @Munn2022, the type of source was not a selection criteria, therefore experimental and qualitative studies, as well as meta-analysis and systematic reviews are included. This allows us to have an idea as complete as possible about the existing literature on cooperation in commons and social dilemmas. Moreover, there were not chronological or geographical limitations, once again to provide a broader vision on the topic. There were however some selection criteria concerning the papers' content. First of all, as mentioned in the introduction, this review will focus on individual and group dynamic that can enhance or decrease cooperation in a social dilemma situation (i. e. commons). For this reason, all the papers investigating how an external entity/institution can shape cooperation were not included. Secondly, papers that studied social dilemmas with an agent-based model methodology were also excluded. **include explication**

@@

# Individual factors

## Gender

The effect of gender on cooperation is controversial, and studies that investigated it provided contradictory results: sometimes men cooperated more [@Dorrough2019], sometimes women did [@Peshkovskaya2017], and sometimes there was no difference between genders. In general, meta-analysis found a non significant effect size for this difference [e.g. @Balliet2011; @Spadaro2023]. This indicates that gender differences in cooperation are very flexible and can vary depending on the context [@Spadaro2023]. Therefore, when a significant effect is observed, it means that gender has somewhat been made salient by the situation [@Sell2009].

@@

## Group identity

@Gomez-Ruiz2020: even if study about gender differences, they found a main effect of team identity on cooperation
@Arora2016: baseline = reciprocity: participants respond with defection to defection and with cooperation to cooperation, but in-group identification can change this --> main effect of identification on cooperation
faced to an in-group defector, high identifiers cooperate more than low (no difference between high and low when the partner cooperates) = compensation + this compensation comes with lower trust toward the partner who defected, so the cooperation is not driven by in-group favoritism
@Torsvik2011: group identity as mediator of anticipating a discussion (see if useful or not to add it here)
@VanVugt2009: mention that it happens that high-identifying members compensate for free-riders + when people identify with a social group the are more concerned about their in-group reputation
boost of social identity through inducing competition between groups, but not helpful --> promote a superordinate social identity
group member that strongly identify with their community do not need an economic incentive to cooperate
@Puurtinen2009: between group competition enhances cooperation (even between unrelated individuals) by aligning individual and group interest --> investements in public good higher in the group competition vs normal condition + in the group competition there was more anger toward in-group free-rider and guilt toward its own lack of cooperation --> ingroup identification can be enhanced via intergroup competition
@Noonan2016: study about commons = dog parks --> "having a strong sens of community is related to increased voluntarism" + re-read to see if others parts could be interesting
@Zhang2019: collective risk as operationalization of group identity: (1) cooperation decreased with time when the risk was individual, but not when it was collective; (2) beliefs about others' cooperation formed similarly under the two conditions = these beliefs are interpreted in a different way according to the condition
@Dorrough2015: ingroup favoritism increase with time and it is mediated by expectations of others' contributions + the increment is due to the change between ingroup and outgroup as interaction partners, it is not gradual

@Bardsley2005: paper about conformity (see if it can be useful in this section)

#D
